\documentclass[./main.tex]{subfiles}

\begin{document}

\chapter{People}

\chapter{Wild Things}

\chapter{Eldritch Gods}

% if you wish to reference this creature in another file, use the following command
% \hyperref[monster:name]{reference}

\chapter{Eldritch Creatures}
% You can optionally not include the background by saying
% begin{monsterboxnobg}
\begin{monsterbox}{Monster Foo}\label{monster:foo}
  \begin{hangingpar}
    \textit{Small metasyntactic variable (goblinoid), neutral evil}
  \end{hangingpar}
	\dndline%
	\basics[%
	armorclass = 12,
	hitpoints  = \dice{3d8 + 3},
	speed      = 50 ft
	]
	\dndline%
	\stats[
    STR = \stat{12}, % This stat command will autocomplete the modifier for you
    DEX = \stat{7}
	]
	\dndline%
	\details[%
	% If you want to use commas in these chapters, enclose the
	% description in braces.
	% I'm so sorry.
	languages = {Common Lisp, Erlang}, 
% 	senses = Darkvision, challenge = 4
	]
	\dndline%
	\begin{monsteraction}[Monster-super-powers]
		This Monster has some serious superpowers!
	\end{monsteraction}
	\monstersection{Actions}
	\begin{monsteraction}[Generate text]
		This one can generate tremendous amounts of text! Though only when it wants to.
	\end{monsteraction}

	\begin{monsteraction}[More actions]
    See, here he goes again! Yet more text.
	\end{monsteraction}
\end{monsterbox}

\begin{monsterbox}{Cave Beast}\label{monster:foo}
  \begin{hangingpar}
    \textit{Large cave dweller, neutral evil}
  \end{hangingpar}
	\dndline%
	\basics[%
	armorclass = 14,
	hitpoints  = \dice{8d12 + 10},
	speed      = 30 ft
	]
	\dndline%
	\stats[
    STR = \stat{18}, % This stat command will autocomplete the modifier for you
    DEX = \stat{12},
    INT = \stat{8},
    CON = \stat{12},
    WIS = \stat{8},
    CHA = \stat{2}
	]
	\dndline%
	\details[%
	% If you want to use commas in these chapters, enclose the
	% description in braces.
	languages = {Deep Speech}, 
 	senses = Blindsight 30 ft., challenge = 4,
 	skills = Perception (+6),
	]
	\dndline%
	\begin{monsteraction}[Cave Sense]
	    When underground in their natural habitat, cave beasts gain advantage on perception checks.
	\end{monsteraction}
	\begin{monsteraction}[Thick Skin]
	    Due to their adaptation to their home, cave beasts have resistance to cold damage.
	\end{monsteraction}
	\begin{monsteraction}[Light Sensitivity]
	    When subjected to bright light, cave beasts suffer disadvantage on their attack roles. In addition, they are vulnerable to radiant damage.
	\end{monsteraction}
	\monstersection{Actions}
	\begin{monsteraction}[Extinguish Light]
        Twice per encounter, the cave beast can release a wave of dark energy that extinguishes all non-magical light sources and any magical light sources of level 1 or lower.
	\end{monsteraction}
	\begin{monsteraction}[Multi-attack]
		Each turn, the cave beast can make two claw attacks.
	\end{monsteraction}
	\begin{monsteraction}[Claw attack]
	    The cave beast takes a swipe against an enemy with its long sharp nails (+5 to hit, 2d10 + 6)
	\end{monsteraction}
\end{monsterbox}
\end{document}