\documentclass[./main.tex]{subfiles}
 
\begin{document}

\textit{Shadows dance in the alleyways, a strangely viscous consistency to their movements. Small, skittering horrors creep along the ceilings, frightening children and filling the air with their chittering calls. Bands of cultist marauders stalk the streets, having abandoned their own kind in favor of a new, more terrible overlord. This is Boston 30--, a thousand years after the Awakening.}

\textit{Not so far from today, magic was reawakened in the world. Eldritch horrors long sleeping awoke, and with their reemergence came an explosion of magical energy. Humanity was transformed -- some of them literally. Certain bloodlines, their Eldritch past long forgotten, woke to a transformed existence. The Eldritch calling boiled in their blood, and their bodies warped and changed into different magical races.}

\textit{Even those whose bodies remained unchanged were not left entirely whole. Those who were particularly magically sensitive developed strange new abilities which we might call magic. Some used these powers for good, and others for evil. Before society could fully adapt to these changes, the Invasion began.}

\textit{It started with small things. People reported strange sounds down alleyways, sightings of moving shadows in the daylight. Then, people started to go missing, swallowed up by the darkness of untold horrors. We ignored these warnings for what they were, and continued to bicker amongst ourselves like spoiled children. We should have known it was going to get worse.}

\textit{Comets began to land, all around the world, harbingers of our destruction. These strange new metals seemed to shift between realities, emitting an entirely new kind of energy. Wherever they landed, a stream of dark horrors streamed forth, an incessant wave of true terror. It was over in days, but lasted much longer.}

\textit{All organized resistance quickly crumbled before the repeated and powerful assaults of the Eldritch horde. Even as reports began to trickle in, tall tales of ordinary men and women turned into monstrous things, we were forced beneath the streets.} 

\textit{Concealed by the same shadows which were once the devilish highway of our adversaries, we waited, and rebuilt what we could.}

\textit{In time, scouts sent to the surface began to return unmenaced, and we began to believe the world above could be ours once again.}

\textit{The Outer Gods returned to their slumber; we must take this chance to reclaim a foothold above, and drive what horrors remain back to their unholy residence.}


\end{document}