\documentclass[././main.tex]{subfiles}
\begin{document}

\section{Orders}
Orders exist outside the boundaries of established settlements with a single purpose: protect humanity as a whole from the terrors of the night.

\subsection{Blood Hunters (Order of the Abomination)}
The Blood Hunters are a dispersed order who roam from settlement to settlement taking bounties on eldritch beasts. In order to accomplish this, each blood hunter takes in the essence of an eldritch beast, morphing physically and spiritually as they master their tainted blood to become stronger than before.

While the peoples of Boston appreciate and respect the work done by blood hunters, they are generally greeted with some disgust and superstitious distrust. Because of this, most hunters live a solitary, nomadic life as they move from town to town before wearing out their welcome. However, larger settlements have been known to keep a blood hunter in residence to handle and advise on eldritch issues as they arise.

\subsection{Order of the Yellow Sign}

\subsection{Moon Mother's Maidens}
A secretive organization, the maidens are rarely seen in groups outside of their sacred grove in the ruins of the Harvard Arboretum. However, designated seekers are constantly roving the wastes beyond Boston in search of magical energy to fuel their enigmatic project. In the course of this search, they have found a variety of magical items, and the seekers who wield them are known to be formidable magical warriors. 

In the depths of their grove, it is rumored that they are close to completing a ritual centuries in the making. The maidens believe that through this ritual they will be able to summon the Moon Mother from her native realm and heal the world's aching wounds. 


\end{document}