\documentclass[././main.tex]{subfiles}
\begin{document}
\section{Gadgets}
Artifacts of the Old World; new inventions blending magic and technology; however you draw the line, Gadgets are more special than the average item and may require special experience to use.


\dndgadget[Requires \textit{Dangerous Equipment} to wield proficiently]{Stun Gauntlet}{Uncommon; Dangerous}{An artifact from the old world that still sparks with condensed lightning. Melee unarmed assist, 2d6 lightning damage}

\dndgadget[Because anyone with a radio can receive these messages, different factions have created increasingly complex codes to mask their messages leading to a continuous arms race between codetalkers and codebreakers.]{Two-Way Radio}{Common}{With this item, you can transmit or receive a message out over the airwaves to anyone using a radio within 5 miles.}

\dndgadget[]{Entangled Speakers}{Rare}{These speakers glow red with eldritch energy, and they each constantly emit the sounds surrounding their companion speaker. The devices emit the sounds at the exact same volume as they reach the companion device, and there is no apparent way to turn them off short of breaking them. Notably, there is no distance at which this communication is severed, and they can transmit even between planes.}

\dndgadget[]{Form Stealer}{Very Rare}{With this device, the user can take a photo of a subject, store it, and at any later time release an eldritch apparition mimicking the subject's appearance and voice. This apparition will take verbal orders from the user and can speak, move, and interact with electronics, however they cannot interact with any physical object. The user can use the camera's display to watch through the eyes of the apparition, and at any point pressing the power button on the camera will cause the apparition to dissipate.}

\dndgadget[]{Night Vision Goggles}{Uncommon}{Wearing these goggles provides the user with darkvision out to 30 feet.}


\end{document}