% change '././main.tex' below to reflect sub-document's position in folder hierarchy
\documentclass[././main.tex]{subfiles}
 
\begin{document}

\begin{dndclass}{Shadow Tinkerer}{Shadow Tinkerers forget more about gadgetry than most folks will ever learn. These masters of gears and pulleys hit hard using traps, gadgets, and restored artifacts of the Old World. Whether it's carefully sabotaging a shipment of goods or finding just the right time to incapacitate an enemy, the Shadow Tinkerer is a force to be reckoned with.}
\narrative{"Most folks," Arn-Tholn began, twirling a grease-blackened wrench around one long, elvish finger, "don't think too hard about what goes into what they use." Deft hands worked faster than she spoke, pushing tiny metal bits into exactly the right place. Cover, secure, test. A little to the left. Orn watched as she rolled to the other corner of her tiny workshop, fishing for just the right esoteric part to make complete her invention.
\newline
"Is that so? And you're telling me you're the sort to do that kind of thinking." Orn rumbled, the strange consonants of the Common dialect rolling uncomfortably over a tongue used to the simple beauty of the Orcish language. The elf clicked her tongue in a sort of annoyed confirmation, delving deeper into the mechanics of the small disk she was working on.
\newline
"That would be my point, indeed." With a final click and a satisfied sound, she rolled over to her large guest. Handing the disk to him, she waved the same wrench over towards the door. "Try that out. You're used to throwing, right? See if you can get it into that dumpster." Orn hefted the small thing, dwarfed by his hand, and raised an eyebrow.
\newline
"This thing is supposed to get me in to the grand bank?"
\newline
"Yes. Now throw!" She gestured again. Skeptical, Orn did as she asked, throwing the disk in a nice arc towards the dumpster about a hundred feet away.
\newline
Even at such a distance, he could feel the incredible heat of the explosion as if it were right in front of him. The dumpster erupted in a massive fireball, making him glad that they were in an abandoned part of town. He turned to the now-smiling elf, her eyes glittering with amusement -- and something darker -- as she held another of the devices out to him.
\newline
"Now, I believe we were about to discuss payment?"}

\classfeature{Tinkerer}{Starting when you assume this archetype at 3rd level, you may spend a short rest Tinkering with a weapon or item in your possession. The die to roll, and the outcome it results in, are detailed in the table below.}

\classfeature{Gadgeteer}{Starting at 3rd level, you may spend a short rest constructing a Trap or repairing a Gadget. You also gain one Uncommon or Common Gadget selected from the table located in the Items section of this expansion.}

\classfeature{One with the Shadows}{Starting at 5th level, you may use this ability once per short rest to blend into the shadows around you. You gain advantage on Stealth rolls against creatures without dark vision and gain an additional 10 ft of movement speed. At 14th level this ability works against creatures with dark vision as well.

At 7th level you may make a short range teleport between shadowed areas no more than 20 feet apart. At 12th level this range increases to 40 feet.}

\classfeature{Mechanically Inclined}{Starting at 3rd level, you immediately gain knowledge of a school of Mechanical Workings chosen from the table below. You may wield any weapon from that school proficiently and gain advantage on checks involving that particular school of knowledge.}

\begin{dndtable}
   School of Knowledge  & Checks \\
   Physics              & physical things\\
\end{dndtable}

\end{dndclass}

\end{document}