\documentclass[././main.tex]{subfiles}

\begin{document}
\section{Providence}

In the ruins of Providence, RI, an empire has risen from the ashes. Centered on the old campus of Brown University, the empire has multiple outlying communities who pay tribute and provide the soldiers necessary for aggressive military expansion. The political environment of the empire is defined by cutthroat competition between these communities in order to gain the favor of the central government. 

When this backstabbing neared all-out civil war several decades ago, the emperor instituted a formal competition between them to focus their efforts. This resulted in an event every five years where each community sends forth a battalion of their finest soldiers to compete in a battle to the death. The winner is awarded the chalice of command which gives them the right to elect one of their own as the Empress's right hand to manage domestic affairs while he leads the army of Providence on crusade.

The empress, also known as "The Hand", is the enigmatic divine avatar of Lykor the god of unity and order. Standing over six feet with ivory wings tipped in gold, she is an aasimar with dark skin, eyes of solid gold, and veins of ruby running throughout her body. 

Not all within the empire are content with the status quo however, and whispers have been building of a secretive group who seeks the dissolution of the empire. In the cover of night, this group worships the god Erkor who preaches a gospel of freedom and individual choice. During the daytime, they hold positions up and down the power structure of the empire while they subtly stoke the tensions constantly bubbling beneath the surface.

\subsection{Erkor and Lykor's Divine Parentage}
Unbeknownst to their followers, Erkor and Lykor are both simply servants to a greater eldritch being who feeds off of the infighting of his followers. 

\end{document}