\documentclass[././main.tex]{subfiles}

\begin{document}
\section{The Fens}
Centered on the ruins of Fenway, The Fens is a wealthy settlement with relatively few long-term residents, but a steady flow of travelers seeking thrills and riches. The heart of the settlement is an arena where the foolhardy try their luck against eldritch beasts of all kinds. Surrounding this competition, a series of gambling establishments cater to the other travelers. Throughout the entirety of The Fen, an aura of confidence and hope infects the minds of its residents. Under this magical influence, those who come to The Fen take extraordinary risks with their lives and livelihoods, either leaving with their heart's desire fulfilled or more frequently not leaving at all. 

The center of this magical projection is the infectiously charismatic and equally enigmatic Red. She can often be seen leading the festivities from the balcony of her palace built into the stands. She has been heard to make dangerous bets with the leaders and warlords in the greater boston area offering grand rewards if an impossible task can be completed; however, should they fail to complete the task, they are branded with her mark to be called upon at a later date. If one looks closely, many of the permanent residents who run the various establishments of the Fens can be seen to bear this mark.

Little is known of the origins of Red, as both she and the Fens have existed for at least the last few hundred years. However, whispers surrounding her eldritch connections are near constant, and much debate occurs behind closed doors as to whether her nature is fully eldritch or is merely that of an extremely powerful magic user.


\end{document}